Why is it that statistical tests for residuals are not widely used? An explanation using visual inference.

### 2023-01-30 paper_comparison/paper_comparison/paper_comparison.Rmd
clarify the usage of the experimental data

As mentioned in Section \ref{calculating-p-values-for-the-visual-test}, $\alpha$ used in Equation \ref{eq:pvalue-beta-binomial} needs to be estimated using null lineups. Hence, 36 lineups with all combinations of $n$ and $X_{raw}$ and three replications are included in experiment III. In these lineups, the data of the data plot is generated from a model with zero effect size, while the data of the 19 null plots are generated using the same simulation method discussed in Section \ref{sampling-from-the-null-distribution}. This generation procedure differs from the canonical Rorschach lineup procedure, which requires that all 20 plots are generated from the null hypothesis. However, these lineups serve the same fundamental purpose: to assess the number of visually interesting plots generated under the null hypothesis.

@@

There are `r 160 * 18`, `r 150 * 18` and `r 133 * 18` lineups evaluation made by 160, 150 and 133 subjects recruited for experiment I, II and III respectively. In the total of `r nrow(filter(vi_survey, !attention_check))` lineup evaluations, `r nrow(filter(vi_survey, type == "polynomial", !attention_check))` use lineups produced by the non-linearity model, `r nrow(filter(vi_survey, type == "heteroskedasticity", !attention_check))` use lineups produced by the heteroskedasticity model, and `r nrow(filter(vi_survey, null_lineup, !attention_check))` use null lineups. Besides, there are `r nrow(filter(vi_survey, attention_check))` attention checks not included in the analysis. The collated dataset is provided in `vi_survey` of the `visage` `R` package.

>>>>

As mentioned in Section \ref{calculating-p-values-for-the-visual-test}, $\alpha$ used in Equation \ref{eq:pvalue-beta-binomial} needs to be estimated using null lineups. Hence, three replications of 36 lineups with all combinations of $n$ and fitted value distributions are included in experiment III. In these lineups, the data of the data plot is generated from a model with zero effect size, while the data of the 19 null plots are generated using the same simulation method discussed in Section \ref{sampling-from-the-null-distribution}. This generation procedure differs from the canonical Rorschach lineup procedure, which requires that all 20 plots are generated from the null hypothesis. However, these lineups serve the same fundamental purpose: to assess the number of visually interesting plots generated under the null hypothesis.

@@

There are `r 160 * 18`, `r 150 * 18` and `r 133 * 18 - nrow(filter(vi_survey, null_lineup, !attention_check))` lineups evaluation made by 160, 150 and 133 subjects recruited for experiment I, II and III respectively. In the total of `r nrow(filter(vi_survey, !attention_check))` lineup evaluations, `r nrow(filter(vi_survey, type == "polynomial", !attention_check))` use lineups produced by the non-linearity model, and `r nrow(filter(vi_survey, type == "heteroskedasticity", !attention_check))` use lineups produced by the heteroskedasticity model. Besides, there are `r nrow(filter(vi_survey, attention_check))` attention checks and `r nrow(filter(vi_survey, null_lineup, !attention_check))` evaluations on null lineups needed for the estimate of $\alpha$ not included in the analysis. The collated dataset is provided in `vi_survey` of the `visage` `R` package.

### 2023-01-30 paper_comparison/paper_comparison/paper_comparison.tex
clarify the usage of the experimental data

As mentioned in Section \ref{calculating-p-values-for-the-visual-test},
\(\alpha\) used in Equation \ref{eq:pvalue-beta-binomial} needs to be
estimated using null lineups. Hence, 36 lineups with all combinations of
\(n\) and \(X_{raw}\) and three replications are included in experiment
III. In these lineups, the data of the data plot is generated from a
model with zero effect size, while the data of the 19 null plots are
generated using the same simulation method discussed in Section
\ref{sampling-from-the-null-distribution}. This generation procedure
differs from the canonical Rorschach lineup procedure, which requires
that all 20 plots are generated from the null hypothesis. However, these
lineups serve the same fundamental purpose: to assess the number of
visually interesting plots generated under the null hypothesis.

@@

There are 2880, 2700 and 2394 lineups evaluation made by 160, 150 and
133 subjects recruited for experiment I, II and III respectively. In the
total of 7974 lineup evaluations, 3744 use lineups produced by the
non-linearity model, 4230 use lineups produced by the heteroskedasticity
model, and 720 use null lineups. Besides, there are 886 attention checks
not included in the analysis. The collated dataset is provided in
\texttt{vi\_survey} of the \texttt{visage} \texttt{R} package.

>>>>

As mentioned in Section \ref{calculating-p-values-for-the-visual-test},
\(\alpha\) used in Equation \ref{eq:pvalue-beta-binomial} needs to be
estimated using null lineups. Hence, three replications of 36 lineups
with all combinations of \(n\) and fitted value distributions are
included in experiment III. In these lineups, the data of the data plot
is generated from a model with zero effect size, while the data of the
19 null plots are generated using the same simulation method discussed
in Section \ref{sampling-from-the-null-distribution}. This generation
procedure differs from the canonical Rorschach lineup procedure, which
requires that all 20 plots are generated from the null hypothesis.
However, these lineups serve the same fundamental purpose: to assess the
number of visually interesting plots generated under the null
hypothesis.

@@

There are 2880, 2700 and 1674 lineups evaluation made by 160, 150 and
133 subjects recruited for experiment I, II and III respectively. In the
total of 7974 lineup evaluations, 3744 use lineups produced by the
non-linearity model, and 4230 use lineups produced by the
heteroskedasticity model. Besides, there are 886 attention checks and
720 evaluations on null lineups needed for the estimate of \(\alpha\)
not included in the analysis. The collated dataset is provided in
\texttt{vi\_survey} of the \texttt{visage} \texttt{R} package.
